Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-27 document/ms.tex
a few more citations
citing the people that need to be cited

Given this parameterized rate $\obs{\rate}_\ratepars$, we can compute the
Poisson likelihood of a \catalog\ (see Appendix XXXXX for the derivation)
\begin{eqnarray}\eqlabel{true-like}
\ln p(\catalog\,|\,\ratepars) &\propto&
\sum_{k=1}^K \ln\obs{\rate}_\ratepars (\entry_k)
- \int \obs{\rate}_\ratepars (\entry) \dd\entry
\end{eqnarray}
where we have assumed that every object in \catalog\ is an independent
Poisson sample from the rate.

@@

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright
\bibitem[Brewer \& Stello(2009)]{brewer}
Brewer, B.~J., \& Stello, D.\ 2009, \mnras, 395, 2226 (\arxiv{0902.3907})
\bibitem[Carter \& Winn(2009)]{carter}
Carter, J.~A., \& Winn, J.~N.\ 2009, \apj, 704, 51 (\arxiv{0909.0747})
\bibitem[Dong \& Zhu(2013)]{dong}
Dong, S., \& Zhu, Z.\ 2013, \apj, 778, 53 (\arxiv{1212.4853})
\bibitem[Hogg \etal(2013)]{hoggwhitepaper}
Hogg, D.~W., Angus, R., Barclay, T., et al.\ 2013, \arxiv{1309.0653}
\bibitem[Hogg \etal(2010)]{hogge}
Hogg, D.~W., Myers, A.~D., \& Bovy, J.\ 2010, \apj, 725, 2166 (\arxiv{1008.4146})
\bibitem[Petigura \etal(2013)]{petigura}
Petigura, E.~A., Howard, A.~W., \& Marcy, G.~W.\ 2013,
Proceedings of the National Academy of Science, 110, 19273 (\arxiv{1311.6806})
\bibitem[Roberts \etal(2013)]{roberts}
Roberts, S., McQuillan, A., Reece, S., \& Aigrain, S.\ 2013, \mnras, 435, 3639 (\arxiv{1308.3644})
\end{thebibliography}

>>>>

Given this parameterized rate $\obs{\rate}_\ratepars$, we can compute the
Poisson likelihood of a \catalog\ (\citealt{tabachnik,youdin,dong})
\begin{eqnarray}\eqlabel{true-like}
\ln p(\catalog\,|\,\ratepars) &\propto&
\sum_{k=1}^K \ln\obs{\rate}_\ratepars (\entry_k)
- \int \obs{\rate}_\ratepars (\entry) \dd\entry
\end{eqnarray}
where we have assumed that every object in \catalog\ is an independent
Poisson sample from the rate.

@@

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright

\bibitem[Brewer \& Stello(2009)]{brewer}
Brewer, B.~J., \& Stello, D.\ 2009, \mnras, 395, 2226 (\arxiv{0902.3907})

\bibitem[Carter \& Winn(2009)]{carter}
Carter, J.~A., \& Winn, J.~N.\ 2009, \apj, 704, 51 (\arxiv{0909.0747})

\bibitem[Dong \& Zhu(2013)]{dong}
Dong, S., \& Zhu, Z.\ 2013, \apj, 778, 53 (\arxiv{1212.4853})

\bibitem[Hogg \etal(2013)]{hoggwhitepaper}
Hogg, D.~W., Angus, R., Barclay, T., et al.\ 2013, \arxiv{1309.0653}

\bibitem[Hogg \etal(2010)]{hogge}
Hogg, D.~W., Myers, A.~D., \& Bovy, J.\ 2010, \apj, 725, 2166 (\arxiv{1008.4146})

\bibitem[Petigura \etal(2013)]{petigura}
Petigura, E.~A., Howard, A.~W., \& Marcy, G.~W.\ 2013,
Proceedings of the National Academy of Science, 110, 19273 (\arxiv{1311.6806})

\bibitem[Roberts \etal(2013)]{roberts}
Roberts, S., McQuillan, A., Reece, S., \& Aigrain, S.\ 2013, \mnras, 435, 3639
(\arxiv{1308.3644})

\bibitem[Tabachnik \& Tremaine(2002)]{tabachnik}
Tabachnik, S., \& Tremaine, S.\ 2002, \mnras, 335, 151
(\arxiv{astro-ph/0107482})

\bibitem[Youdin(2011)]{youdin}
Youdin, A.~N.\ 2011, \apj, 742, 38 (\arxiv{1105.1782})

\end{thebibliography}
